---
title: "Demographic Summary Additional Report"
subtitle: "Training: Essential Elements"
date: "October - December 2023"

params:
  quarter: "2023Q2"
  training: "EE"

output: 
  html_document:
    df_print: paged
    fig_width: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      cache = FALSE)
```

```{r library, include=FALSE}
library(tidyverse)
library(skimr)
library(janitor)
library(ggthemes)
library(hrbrthemes)
library(readxl)
library(ggtext)
library(ggalt)
library(ragg)
library(systemfonts)
library(gt)
library(knitr)
library(pagedown)
library(dplyr)
library(scales)
library(lubridate)
library(ggplot2)
library(googlesheets4)
```

```{r colors, include=FALSE}
psu_green <- "#6d8d24"
psu_electricgreen <- "#cfd82d"
psu_forestgreen <- "#213921"
psu_blue <- "#008ac1"
psu_lightblue <- "#a5dff9"
psu_sand <- "#e8d3a2"
psu_stone <- "#8a8a67"
psu_yellow <- "#ffc20e"
psu_red <- "#e64927"
psu_orange <- "#f68b1f"
psu_purple <- "#650360"
```

```{r rds file, include=FALSE}
all_demos <- readRDS("data/clean-all-demos.rds") %>% 
  mutate(quarter = str_replace_all(cohort, c("07$|08$|09$" = "Q1", "10$|11$|12$" = "Q2", "01$|02$|03$" = "Q3", "04$|05$|06$" = "Q4")))

day1 <- read_sheet("https://docs.google.com/spreadsheets/d/1aNWF7AojvdaRg7gaxfztgbog13QVfwIcMqOaiAEiDwM/edit#gid=291857743",
                               sheet = "day1") %>% 
  clean_names()
```

```{r number trainees, include=FALSE}
number_trainees <- all_demos %>% 
  filter(quarter == params$quarter,
         training == params$training) %>% 
  count(quarter) %>% 
  pull(n)
```

Number of Trainees in Quarter: **`r number_trainees`**

### Education Level

```{r education level}
education_level <- all_demos %>% 
  select(quarter, training, education) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(education = fct_relevel(education, c("High School/GED", "Some College", "Associates Degree", "BA/BS in non-Social Sciences", "BA/BS in other Social Sciences", "BA/BS in Social Work", "MA/MS in non-Social Sciences", "MA/MS in other Social Sciences", "MA/MS in Social Work"))) %>% 
  count(education) %>% 
  drop_na(education) %>% 
  mutate(percent_total = n/sum(n)) %>%
  mutate(percent_total_formatted = percent(percent_total, accuracy = 1)) %>% 
  mutate(education_pct = str_glue("{education}: {percent_total_formatted}"))

ed_level_BABSOSS <- education_level %>% 
  filter(education == "BA/BS in other Social Sciences")

ed_level_nonBABSOSS <- education_level %>% 
  filter(education != "BA/BS in other Social Sciences")

education_level %>%   
  ggplot(aes(x = percent_total,
             y = education, 
             fill = education)) +
  geom_col(show.legend = FALSE,
           fill = psu_green) +
  geom_text(data = ed_level_nonBABSOSS,
            aes(label = education_pct),
            hjust = -0.02) +
  geom_text(data = ed_level_BABSOSS,
            aes(label = education_pct),
            hjust = 1.02) +
  theme_void() +
  theme(axis.title = element_blank())
```

### Child Welfare Education Program

```{r cwep}
cwep <- all_demos %>% 
  select(quarter, training, cwep_student) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(cwep_student = fct_relevel(cwep_student, c("Yes", "No"))) %>%
  count(cwep_student) %>% 
  drop_na()

cwep %>%  
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(cwep_student = md("**CWEP Student**"),
             n = md("**Number**"))
```

```{r cwep location}
cwep_school <- all_demos %>% 
  select(quarter, training, cwep_student, cwep_grad_location) %>% 
  filter(quarter == params$quarter,
         training == params$training,
         cwep_student == "Yes")
```

```{r cwep_PSU, include=FALSE}
number_cwep_PSU <- if("Portland State University" %in% cwep_school == TRUE){
  cwep_school %>% 
    filter(cwep_grad_location == "Portland State University") %>% 
    count(cwep_grad_location) %>% 
    pull(n)
  } else if ("Portland State University" %in% cwep_school == FALSE){
  print("0")
}
```

Number of Trainees in CWEP at Portland State University: **`r number_cwep_PSU`**

### Current Role

```{r current role}
role <- all_demos %>%
  select(quarter, training, current_role) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(current_role = fct_relevel(current_role, c("Other", "Intern/Student", "Tribal Child Welfare Employee", "Not Assigned Yet", "Certification/Adoption", "Permanency", "CPS", "Screener"))) %>%
  count(current_role) %>% 
  drop_na(current_role) %>% 
  mutate(percent_total = n/sum(n)) %>%
  mutate(percent_total_formatted = percent(percent_total, accuracy = 1)) %>% 
  mutate(role_pct = str_glue("{current_role}: {percent_total_formatted}"))

role_CPS <- role %>% 
  filter(current_role == "CPS")

role_nonCPS <- role %>% 
  filter(current_role != "CPS")

role %>%   
  ggplot(aes(x = percent_total,
             y = current_role, 
             fill = current_role)) +
  geom_col(show.legend = FALSE,
           fill = psu_purple) +
  geom_text(data = role_nonCPS,
            aes(label = role_pct),
            hjust = -0.02) +
  geom_text(data = role_CPS,
            aes(label = role_pct),
            hjust = 1.02,
            color = "white") +
  theme_void() +
  theme(axis.title = element_blank(),
        plot.title = element_markdown(face = "bold"))
```

### Public Child Welfare in Another State

```{r child welfare other state}
cw_other <- all_demos %>% 
  select(quarter, training, cw_other_state) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(cw_other_state = fct_relevel(cw_other_state, c("Yes", "No"))) %>%
  count(cw_other_state) %>% 
  drop_na()

cw_other %>%  
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(cw_other_state = md("**CW in Other State**"),
             n = md("**Number**")) %>% 
  cols_align(align = "center", 
             columns = cw_other_state) %>% 
  cols_align(align = "center", 
             columns = n)
```

```{r length employed cw other state}
cw_other_length <- all_demos %>% 
  select(quarter, training, cw_other_state, length_cw_other_state) %>% 
  filter(quarter == params$quarter,
         training == params$training,
         cw_other_state == "Yes") %>%
  count(length_cw_other_state)

cw_other_length %>%  
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(length_cw_other_state = md("**Time in CW in Other State**"),
             n = md("**Number**")) %>% 
  cols_align(align = "center", 
             columns = length_cw_other_state) %>% 
  cols_align(align = "center", 
             columns = n)
```

\newpage
### Age

```{r age, include=FALSE}
average_age <- all_demos %>% 
  filter(quarter == params$quarter,
         training == params$training) %>% 
  select(quarter, training, age) %>% 
  drop_na(age) %>%
  summarize(avg_age = mean(age)) %>%
  mutate(age_round = round(avg_age,1)) %>% 
  pull(age_round)

age_min <- all_demos %>% 
  select(quarter, training, age) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>% 
  drop_na() %>% 
  summarize(agemin = min(age)) %>% 
  pull(agemin)

age_max <- all_demos %>% 
  select(quarter, training, age) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>% 
  drop_na() %>% 
  summarize(agemax = max(age)) %>% 
  pull(agemax)
```

Average = **`r average_age`** years old  
Minimum = **`r age_min`** years old  
Maximum = **`r age_max`** years old  

### English as Primary Language

```{r english primary language}
eng_prim <- all_demos %>% 
  select(quarter, training, english) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(english = fct_relevel(english, c("Yes", "No"))) %>%
  count(english) %>% 
  drop_na()

eng_prim %>%  
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(english = md("**English Primary Language**"),
             n = md("**Number**")) %>% 
  cols_align(align = "center", 
             columns = english) %>% 
  cols_align(align = "center", 
             columns = n)
```

### Whether or not an SSS1

```{r whether SSS1}
sss1_status <- all_demos %>% 
  select(quarter, training, sss1) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>%
  mutate(sss1 = fct_relevel(sss1, c("Yes", "No"))) %>%
  count(sss1) %>% 
  drop_na()

sss1_status %>%  
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(sss1 = md("**Whether SSS1**"),
             n = md("**Number**")) %>% 
  cols_align(align = "center", 
             columns = sss1) %>% 
  cols_align(align = "center", 
             columns = n)
```

### Time Between Start Date and Training

```{r days to ee prep}
days_to_ee <- all_demos %>%
  select(quarter, training, group_name, start_date) %>%
  left_join(day1) %>% 
  filter(quarter == params$quarter,
         training == params$training) %>% 
  mutate(daystoee = as.numeric(difftime(as.POSIXct(day_one),(as.POSIXct(start_date)), units = "days"))) %>% 
  filter(daystoee >=0 & daystoee<=90)
```


```{r percent within thirty days}
thirty_days <- days_to_ee %>% 
  select(-c(training, group_name)) %>% 
  mutate(thirtydays = if_else(daystoee <= 30, "Yes", "No", missing = NULL)) %>% 
  drop_na() %>% 
  count(thirtydays) %>% 
  filter(thirtydays == "Yes") %>% 
  pull(n)
```

Percentage of Employees who started within *30 days* of hire: **`r scales::label_percent()(thirty_days/number_trainees)`**

```{r percent within forty-five days}
fortyfive_days <- days_to_ee %>% 
  select(-c(training, group_name)) %>% 
  mutate(fortyfivedays = if_else(daystoee <= 45, "Yes", "No", missing = NULL)) %>% 
  drop_na() %>% 
  count(fortyfivedays) %>% 
  filter(fortyfivedays == "Yes") %>% 
  pull(n)
```

Percentage of Employees who started within *45 days* of hire: **`r scales::label_percent()(fortyfive_days/number_trainees)`**

```{r percent within sixty days}
sixty_days <- days_to_ee %>% 
  select(-c(training, group_name)) %>% 
  mutate(sixtydays = if_else(daystoee <= 60, "Yes", "No", missing = NULL)) %>% 
  drop_na() %>% 
  count(sixtydays) %>% 
  filter(sixtydays == "Yes") %>% 
  pull(n)
```

Percentage of Employees who started within *60 days* of hire: **`r scales::label_percent()(sixty_days/number_trainees)`**

```{r avg days to ee plot prep}
avg_days_to_ee <- days_to_ee %>% 
  select(quarter, daystoee) %>% 
  filter(quarter == params$quarter) %>% 
  drop_na() %>% 
  summarize(avg_days_to_ee = mean(daystoee)) %>% 
  mutate(dtee_round = round(avg_days_to_ee)) %>% 
  pull(dtee_round)
```

Average # of Days between Start Date and Training = <span style='color:#e64927'>**`r avg_days_to_ee`**</span>
