---
title: "Inclusion Summary"
subtitle: "Training: Family Conditions"
date: "July-September 2023"

params:
  cohort: "2325Q1"

output: 
  html_document:
    df_print: paged
    fig_width: 8
---
<!-- NEEDED INFORMATION - LOOK HERE
To make this work, we need to change the names of the cohorts of the quarter to the same name.
Do this in the "r excel file" chunk (starting line 67). Change name to YYYYQN (ex. 2325Q1).
Update cohort parameter in YAML to new quarter cohort.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE)
```

```{r library, include=FALSE}
library(tidyverse)
library(skimr)
library(janitor)
library(ggthemes)
library(hrbrthemes)
library(readxl)
library(ggtext)
library(ggalt)
library(ragg)
library(systemfonts)
library(gt)
library(knitr)
library(pagedown)
library(dplyr)
library(scales)
library(lubridate)
library(ggplot2)
library(ggrepel)
```

```{r colors, include=FALSE}
psu_green <- "#6d8d24"
psu_electricgreen <- "#cfd82d"
psu_forestgreen <- "#213921"
psu_blue <- "#008ac1"
psu_lightblue <- "#a5dff9"
psu_sand <- "#e8d3a2"
psu_stone <- "#8a8a67"
psu_yellow <- "#ffc20e"
psu_red <- "#e64927"
psu_orange <- "#f68b1f"
psu_purple <- "#650360"
```

```{r excel file, include=FALSE}
fc_inclusion <- read_excel(path = "I:\\Staff\\GSSW\\SALEM\\DATA ENTRY\\3. Family Conditions\\FC DB 202307.xlsx",
                                   sheet = "overall") %>% 
  clean_names() %>% 
  select(cohort, id_trainer, id_other, id_comment) %>% 
  mutate(cohort = as.character(cohort)) %>% 
  mutate(cohort = if_else(cohort == "202309", "2325Q1", cohort))
```

```{r number respondents, include=FALSE}
number_respondents_inclusion <- fc_inclusion %>% 
  filter(cohort == params$cohort) %>% 
  count(cohort) %>% 
  pull(n)
```

Number of Respondents in Quarter: **`r number_respondents_inclusion`**

```{r}
fc_inclusion_scales <- fc_inclusion %>%
  select(-id_comment) %>% 
  pivot_longer(cols = -cohort,
               names_to = "scale",
               values_to = "rating",
               values_drop_na = TRUE)
```

```{r trainer rating prep}
avg_trainers <- fc_inclusion_scales %>%
  filter(cohort == params$cohort,
         scale == "id_trainer") %>%
  drop_na() %>% 
  summarize(avg_trainers = mean(rating)) %>% 
  mutate(rating_round = round(avg_trainers,1)) %>%
  pull(rating_round)
```

$~$

$~$

#### I felt respected based on my identities by <span style = 'color: #008ac1'>trainers/staff</span>
7-point anchored scale from Not at all Respected to Extremely Respected

Average = **`r avg_trainers`**

```{r trainers, fig.height = 2, fig.width = 7}
fc_inclusion_scales %>%
  filter(cohort == params$cohort,
         scale == "id_trainer") %>% 
  drop_na() %>% 
  count(cohort, scale, rating) %>% 
  mutate(pct = n / sum(n)) %>%
  mutate(pct_display = str_glue("{rating} ({percent(pct, accuracy = 1)})")) %>% 
  ggplot(aes(x = pct,
             y = cohort,
             fill = rating)) +
  scale_fill_gradient2(limits = c(1,7),
                      low = psu_red,
                      mid = psu_sand,
                      high = psu_forestgreen,
                      midpoint = 4,
                      space = "Lab",
                      guide = "colorbar",
                      aesthetics = "fill") +
  geom_col(show.legend = TRUE,
           position = "fill",
           width = 0.5) +
  geom_text_repel(aes(label = pct_display),
            color = "white",
            size = 4,
            position = position_fill(vjust = 0.5),
            min.segment.length = 0.2) +
  scale_x_continuous(expand = expansion(add = c(0,0.2)),
                     labels = NULL) +
  scale_y_discrete(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold"))
```

```{r peer rating prep}
avg_peers <- fc_inclusion_scales %>%
  filter(cohort == params$cohort,
         scale == "id_other") %>%
  drop_na() %>% 
  summarize(avg_peers = mean(rating)) %>% 
  mutate(rating_round = round(avg_peers,1)) %>%
  pull(rating_round)
```

$~$

#### I felt respected based on my identities by <span style = 'color: #650360'>peers</span>
7-point anchored scale from Not at all Respected to Extremely Respected

Average = **`r avg_peers`**

```{r peers, fig.height = 2, fig.width = 7}
fc_inclusion_scales %>%
  filter(cohort == params$cohort,
         scale == "id_other") %>% 
  drop_na() %>% 
  count(cohort, scale, rating) %>% 
  mutate(pct = n / sum(n)) %>%
  mutate(pct_display = str_glue("{rating} ({percent(pct, accuracy = 1)})")) %>% 
  ggplot(aes(x = pct,
             y = cohort,
             fill = rating)) +
  scale_fill_gradient2(limits = c(1,7),
                      low = psu_red,
                      mid = psu_sand,
                      high = psu_forestgreen,
                      midpoint = 4,
                      space = "Lab",
                      guide = "colorbar",
                      aesthetics = "fill") +
  geom_col(show.legend = TRUE,
           position = "fill",
           width = 0.5) +
  geom_text_repel(aes(label = pct_display),
            color = "white",
            size = 4,
            position = position_fill(vjust = 0.5),
            min.segment.length = 0.2) +
  scale_x_continuous(expand = expansion(add = c(0,0.2)),
                     labels = NULL) +
  scale_y_discrete(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold"))
```

\newpage

### Open-Ended Question Responses

*Responses on Scale Questions*

```{r high end responses}
fc_inclusion %>% 
  filter(cohort == params$cohort,
         id_trainer %in% c("5", "6", "7")|id_other %in% c("5", "6", "7")) %>% 
  select(id_comment) %>% 
  drop_na()  %>% 
  distinct() %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(
    id_comment = md("**Corresponding Responses for Ratings of 5, 6, or 7**"))
```

```{r middle response}
fc_inclusion %>% 
  filter(cohort == params$cohort,
         id_trainer == "4"|id_other == "4") %>% 
  select(id_comment) %>% 
  drop_na()  %>% 
  distinct() %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(
    id_comment = md("**Corresponding Responses for Ratings of 4**"))
```

```{r low end responses}
fc_inclusion %>% 
  filter(cohort == params$cohort,
         id_trainer %in% c("1", "2", "3")|id_other %in% c("1", "2", "3")) %>% 
  select(id_comment) %>% 
  drop_na()  %>% 
  distinct() %>% 
  gt() %>% 
  tab_options(table.align = "left") %>% 
  cols_label(
    id_comment = md("**Corresponding Responses for Ratings of 1, 2, or 3**"))
```