---
title: "Inclusion Summary"
subtitle: "Training: Certification and Adoption Worker Training"
date: "October - December 2023"

params:
  quarter: "2023Q2"
  training: "EE"

output: 
  html_document:
    df_print: paged
    fig_width: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE)
```

```{r library, include=FALSE}
library(tidyverse)
library(skimr)
library(janitor)
library(ggthemes)
library(hrbrthemes)
library(ggtext)
library(ggalt)
library(ragg)
library(systemfonts)
library(gt)
library(knitr)
library(pagedown)
library(dplyr)
library(scales)
library(lubridate)
library(ggplot2)
library(ggrepel)
library(googledrive)
library(googlesheets4)
library(here)
```

```{r colors, include=FALSE}
psu_green <- "#6d8d24"
psu_electricgreen <- "#cfd82d"
psu_forestgreen <- "#213921"
psu_blue <- "#008ac1"
psu_lightblue <- "#a5dff9"
psu_sand <- "#e8d3a2"
psu_stone <- "#8a8a67"
psu_yellow <- "#ffc20e"
psu_red <- "#e64927"
psu_orange <- "#f68b1f"
psu_purple <- "#650360"
```

```{r import and filter rds files, include=FALSE}
filter_session_data <- function(raw_data) {
  raw_data %>% 
    filter(training_name == params$training) %>% 
    filter(quarter == params$quarter)
}

id_ratings_filtered <-
  read_rds(here("data/id_ratings.rds")) %>% 
  filter_session_data()

id_qual_comments_filtered <-
  read_rds(here("data/id_qual_comments.rds")) %>% 
  filter_session_data()

id_qual_codes_filtered <-
  read_rds(here("data/id_qual_codes.rds")) %>% 
  filter_session_data()

number_registered_filtered <-
  read_rds(here("data/number_registered.rds")) %>% 
  filter_session_data()
```

```{r number respondents, include=FALSE}
number_respondents_inclusion <- id_ratings_filtered %>% 
  distinct(response_id, quarter) %>% 
  count(quarter) %>% 
  pull(n)
```

Number of Respondents in Quarter: **`r number_respondents_inclusion`**

```{r trainer rating prep}
avg_trainers <- id_ratings_filtered %>%
  filter(question == "id_trainer") %>%
  drop_na() %>% 
  summarize(avg_trainers = mean(rating)) %>% 
  mutate(rating_round = round(avg_trainers,1)) %>%
  pull(rating_round)
```

$~$

$~$

#### I felt respected based on my identities by <span style = 'color: #008ac1'>trainers/staff</span>
7-point anchored scale from Not at all Respected to Extremely Respected

Average = **`r avg_trainers`**

```{r trainers, fig.height = 2, fig.width = 7}
id_ratings_filtered %>%
  filter(question == "id_trainer") %>% 
  drop_na() %>% 
  count(quarter, question, rating) %>% 
  mutate(pct = n / sum(n)) %>%
  mutate(pct_display = str_glue("{rating} \n({percent(pct, accuracy = 1)})")) %>% 
  ggplot(aes(x = pct,
             y = quarter,
             fill = rating)) +
  scale_fill_gradient2(limits = c(1,7),
                      low = psu_red,
                      mid = psu_sand,
                      high = psu_forestgreen,
                      midpoint = 4,
                      space = "Lab",
                      guide = "colorbar",
                      aesthetics = "fill") +
  geom_col(show.legend = TRUE,
           position = "fill",
           width = 0.5) +
  geom_text(aes(label = pct_display),
            color = "white",
            size = 4,
            position = position_fill(vjust = 0.5),
            check_overlap = TRUE) +
  scale_x_continuous(expand = expansion(add = c(0,0.2)),
                     labels = NULL) +
  scale_y_discrete(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold"))
```

```{r peer rating prep}
avg_peers <- id_ratings_filtered %>%
  filter(question == "id_other") %>%
  drop_na() %>% 
  summarize(avg_peers = mean(rating)) %>% 
  mutate(rating_round = round(avg_peers,1)) %>%
  pull(rating_round)
```

$~$

#### I felt respected based on my identities by <span style = 'color: #650360'>peers</span>
7-point anchored scale from Not at all Respected to Extremely Respected

Average = **`r avg_peers`**

```{r peers, fig.height = 2, fig.width = 7}
id_ratings_filtered %>%
  filter(question == "id_other") %>% 
  drop_na() %>% 
  count(quarter, question, rating) %>% 
  mutate(pct = n / sum(n)) %>%
  mutate(pct_display = str_glue("{rating} \n({percent(pct, accuracy = 1)})")) %>% 
  ggplot(aes(x = pct,
             y = quarter,
             fill = rating)) +
  scale_fill_gradient2(limits = c(1,7),
                      low = psu_red,
                      mid = psu_sand,
                      high = psu_forestgreen,
                      midpoint = 4,
                      space = "Lab",
                      guide = "colorbar",
                      aesthetics = "fill") +
  geom_col(show.legend = TRUE,
           position = "fill",
           width = 0.5) +
  geom_text(aes(label = pct_display),
            color = "white",
            size = 4,
            position = position_fill(vjust = 0.5),
            check_overlap = TRUE) +
  scale_x_continuous(expand = expansion(add = c(0,0.2)),
                     labels = NULL) +
  scale_y_discrete(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold"))
```

\newpage

### Open-Ended Question Responses

```{r positive comment count}
number_positive <- if (sum(str_detect(id_qual_comments_filtered$sentiment, "positive"), na.rm = TRUE) > 0) {
  id_qual_comments_filtered %>%
    filter(str_detect(sentiment, "positive")) %>%
    distinct(id_comment, .keep_all = TRUE) %>% 
    count(quarter) %>%
    pull(n)
} else {
  print("0")
}
```

```{r positive codes count, include=FALSE}
number_positive_codes <- if (sum(str_detect(id_qual_codes_filtered$sentiment, "positive"), na.rm = TRUE) > 0) {
  id_qual_codes_filtered %>%
    filter(str_detect(sentiment, "positive")) %>%
    count(quarter) %>%
    pull(n)
} else {
  print("0")
}
```

#### Positive Responses  
Number of Responses Received: **`r number_positive`**  
Number of Themes Within Comments: **`r number_positive_codes`**

```{r positive prep}
positive_theme_count <- id_qual_codes_filtered %>% 
  filter(str_detect(sentiment, "positive")) %>% 
  count(sub_group) %>% 
  arrange(desc(n))

positive_trainpeer <- positive_theme_count %>% 
  filter(sub_group %in% c("Trainer", "Peer"))

positive_allelse <- positive_theme_count %>% 
  filter(sub_group != "Trainer",
         sub_group != "Peer")
```

```{r positive theme plot, fig.height = 4.5, fig.width = 6.5}
positive_theme_count %>% 
  mutate(subgroup = fct_inorder(sub_group)) %>%
  mutate(subgroup = fct_rev(sub_group)) %>%
  ggplot(aes(x = n,
             y = sub_group, 
             fill = sub_group)) +
  scale_fill_manual(values = c(
                     "General" = psu_stone,
                     "Trainer" = psu_forestgreen,
                     "Peer" = psu_purple,
                     "Classroom Dynamics" = psu_green,
                     "Specific or Individual Interaction" = psu_blue,
                     "Bias" = psu_red,
                     "SOGI" = psu_yellow,
                     "Race/Ethnicity" = psu_orange,
                     "Inclusivity" = psu_sand,
                     "Highlighted Comment" = psu_electricgreen)) +
  geom_col(show.legend = FALSE,
           position = "dodge") +
  geom_text(data = positive_allelse,
              aes(label = n),
              color = "black",
              hjust = 1.1,
              size = 5) +
  geom_text(data = positive_trainpeer,
              aes(label = n),
              color = "white",
              hjust = 1.1,
              size = 5) +
  labs(title = "Common Themes") +
  scale_x_continuous(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold", hjust = -.15))
```

```{r positive responses}
positive_comments <- id_qual_comments_filtered %>% 
  filter(str_detect(sentiment, "positive")) %>% 
  mutate(id_code = as.numeric(id_code)) %>% 
  group_by(response_id) %>% 
  summarise(across(everything(), last))

if (sum(str_detect(positive_comments$id_code, "909.1")) > 0) {
  positive_comments %>% 
    select(id_comment, id_code) %>% 
    gt() %>% 
    tab_options(table.align = "left",
                column_labels.font.size = 20) %>% 
    cols_label(
      id_comment = md("**Comments**")) %>%
    tab_style(
      style = list(cell_text(style = "italic",
                        weight = "bold")
                   ),
      locations = cells_body(
        columns = id_comment,
        rows = id_code >= "909.1"
      )
    ) %>% 
    cols_hide(id_code) %>% 
    tab_source_note(source_note = md("^Bold & italicized notes a highlighted comment"))
} else {
  positive_comments %>%  
    select(id_comment) %>% 
    gt() %>% 
    tab_options(table.align = "left",
                column_labels.font.size = 20) %>% 
    cols_label(
      id_comment = md("**Comments**"))
}
```

\newpage

```{r improve comment count, include=FALSE}
number_improve <- if (sum(str_detect(id_qual_comments_filtered$sentiment, "negative"), na.rm = TRUE) > 0) {
  id_qual_comments_filtered %>%
    filter(str_detect(sentiment, "negative")) %>%
    distinct(id_comment, .keep_all = TRUE) %>% 
    count(quarter) %>%
    pull(n)
} else {
  print("0")
}
```

```{r improve codes count, include=FALSE}
number_improve_codes <- if (sum(str_detect(id_qual_codes_filtered$sentiment, "negative"), na.rm = TRUE) > 0) {
  id_qual_codes_filtered %>%
    filter(str_detect(sentiment, "negative")) %>%
    count(quarter) %>%
    pull(n)
} else {
  print("0")
}
```

#### To Improve Responses  
Number of Responses Received: **`r number_improve`**  
Number of Themes Within Comments: **`r number_improve_codes`**

```{r improve prep}
improve_theme_count <- id_qual_codes_filtered %>% 
  filter(str_detect(sentiment, "negative")) %>% 
  count(sub_group) %>% 
  arrange(desc(n))

improve_trainpeer <- improve_theme_count %>% 
  filter(sub_group %in% c("Trainer", "Peer"))

improve_allelse <- improve_theme_count %>% 
  filter(sub_group != "Trainer",
         sub_group != "Peer")
```

```{r improve theme plot, fig.height = 4.5, fig.width = 6.5}
improve_theme_count %>% 
  mutate(sub_group = fct_inorder(sub_group)) %>%
  mutate(sub_group = fct_rev(sub_group)) %>%
  ggplot(aes(x = n,
             y = sub_group, 
             fill = sub_group)) +
  scale_fill_manual(values = c(
                     "General" = psu_stone,
                     "Trainer" = psu_forestgreen,
                     "Peer" = psu_purple,
                     "Classroom Dynamics" = psu_green,
                     "Specific or Individual Interaction" = psu_blue,
                     "Bias" = psu_red,
                     "SOGI" = psu_yellow,
                     "Race/Ethnicity" = psu_orange,
                     "Inclusivity" = psu_sand,
                     "Highlighted Comment" = psu_electricgreen)) +
  geom_col(show.legend = FALSE,
           position = "dodge") +
  geom_text(data = improve_allelse,
              aes(label = n),
              color = "black",
              hjust = 1.5,
              size = 5) +
  geom_text(data = improve_trainpeer,
              aes(label = n),
              color = "white",
              hjust = 1.5,
              size = 5) +
  labs(title = "Common Themes") +
  scale_x_continuous(labels = NULL) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title = element_blank(),
        plot.title = element_markdown(face = "bold", hjust = .05))
```

```{r improve responses}
improve_comments <- id_qual_comments_filtered %>% 
  filter(str_detect(sentiment, "negative")) %>% 
  mutate(id_code = as.numeric(id_code)) %>% 
  group_by(response_id) %>% 
  summarise(across(everything(), last))

if (sum(str_detect(improve_comments$id_code, "909.2")) > 0) {
  improve_comments %>% 
    select(id_comment, id_code) %>% 
    gt() %>% 
    tab_options(table.align = "left",
                column_labels.font.size = 20) %>% 
    cols_label(
      id_comment = md("**Comments**")) %>%
    tab_style(
      style = list(cell_text(style = "italic",
                        weight = "bold")
                   ),
      locations = cells_body(
        columns = id_comment,
        rows = id_code >= "909.2"
      )
    ) %>% 
    cols_hide(id_code) %>% 
    tab_source_note(source_note = md("^Bold & italicized notes a highlighted comment"))
} else {
  improve_comments %>%  
    select(id_comment) %>% 
    gt() %>% 
    tab_options(table.align = "left",
                column_labels.font.size = 20) %>% 
    cols_label(
      id_comment = md("**Comments**"))
}
```